%& -job-name=CV % Put CV or Resume here to generate output files with these names [Use PDFTeXify]

\newif\ifResume
% Comment the following line to get a full CV version
%\Resumetrue % 2-page Resume Version

\ifResume
    \documentclass[10pt]{article}
\else
    \documentclass[11pt]{article}
\fi

\ifResume
    \def \SectionEndSpace {0.9}
    \def \SectionStartSpace {0.5}
    \def \AfterTitleSpace {0.5}
\else
    \def \SectionEndSpace {1.2}
    \def \SectionStartSpace {0.7}
    \def \AfterTitleSpace {0.7}
\fi

\usepackage{tabularx}
\usepackage[resetlabels]{multibib}
\usepackage{CV}
\usepackage{tweaklist}

\ifResume
    \setlength{\textheight}{9.95in}
    \setlength{\headheight}{-2.85in}
    \newlength{\Vspace}
    \setlength{\Vspace}{1mm}
    \newlength{\WidthSkills}
    \setlength{\WidthSkills}{4.8in}
    \setlength{\textwidth}{6.9in}
    \setlength{\oddsidemargin}{-0.2in}
    \setlength{\evensidemargin}{-0.2in}
\else
    \setlength{\textheight}{9.2in}
    \setlength{\headheight}{-2.35in}
    \newlength{\Vspace}
    \setlength{\Vspace}{2mm}
    \newlength{\WidthSkills}
    \setlength{\WidthSkills}{4.4in}
    \setlength{\textwidth}{6.7in}
    \setlength{\oddsidemargin}{-0.1in}
    \setlength{\evensidemargin}{-0.1in}
\fi

\newlength{\VspacePub}
\setlength{\VspacePub}{3mm}

\setlength{\topmargin}{0.0in}
\setlength{\headsep}{2.3in}

\renewcommand{\enumhook}{\setlength{\topsep}{0pt}
  \setlength{\itemsep}{0pt}}

\renewcommand{\itemhook}{\setlength{\topsep}{0pt}
  \setlength{\itemsep}{0pt}}

\renewcommand{\descripthook}{\setlength{\topsep}{0pt}
  \setlength{\itemsep}{0pt}}

\usepackage[pdfpagemode={UseOutlines},bookmarks,bookmarksopen,]{hyperref}
\hyphenation{Isfahan Iran comm-un-ic-ations net-work net-works spec-trometer auto-mobile tech-nology
             LabVIEW MATLAB Simulink OrCAD Xilinx EPANET Embedded Workbench Photoshop CorelDRAW Active Bluetooth}

\begin{document}

\thispagestyle{empty}

\begin{center}

%\ifResume
%    \huge{\textsc{R\'{e}sum\'{e}}}
%
%\else
%    \huge{\textsc{Curriculum Vitae}}
%\fi

{\huge{\textsc{Koosha Marashi}}}

\end{center}

\section{Contact Information}

\begin{flushleft}

    Missouri University of Science and Technology (Missouri S\&T)\\
    113 Engineering Research Lab \\
    500 W. 16th St. \\
    Rolla, MO 65409-6522 \\
    Phone: (573) 202-8465 \\
    E-mail: km89f@mst.edu \\
    Web page: \url{http://www.mst.edu/\~km89f} \\
    Linkedin: \url{http://www.linkedin.com/in/koosham}

\end{flushleft}

\section{Education}

\begin{CV}

\item[8/2012--Present] \textbf{Ph.D. in Computer Engineering} (anticipated graduation date: 5/2017)\\Missouri S\&T, Rolla, MO \\
    Thesis: \emph{Modeling and Analysis of Cyber-Physical Systems:\\Dependability of Critical Infrastructures} \\
    Advisor: Dr. Sahra Sedigh Sarvestani \\
    \textbf{GPA: 3.83/4.0}

\item[9/2006--2/2011] \textbf{B.S. in Electrical Engineering} \\ Isfahan University of Technology, Isfahan, Iran \\
    \textbf{GPA: 15.61/20}

\end{CV}

\section{Work Experience}

\begin{CV}

\item[9/2012--Present] \textbf{\textit{Graduate Research/Teaching Assistant}} \\
    \textit{Missouri S\&T, Department of Electrical and Computer Engineering, Rolla, MO}\vspace{\Vspace} \\
    Developed reliability and survivability models for critical infrastructures. \\
    Proposed a model for quantification of interdependencies in cyber-physical systems. \\
    %Made a VLF signal detector for underwater communications.
    %Graded homework and examinations for \emph{Digital Networks Design} course (CpE-319).

\item[5/2016--8/2016] \textbf{\textit{Software/Hardware Development Intern}} \\
    \textit{Kalscott Eng., Lawrence, KS}\vspace{\Vspace} \\
    Worked on an automated air-band radio for UAVs. Main tasks include migrating to a Linux-powered single-board computer and adding speech recognition feature.

\item[5/2015--8/2015] \textbf{\textit{Web/Application Development Intern}} \\
    \textit{Intellispeak LLC, Lawrence, KS}\vspace{\Vspace} \\
    Developed an information network for e-health services based on Gimbal Bluetooth beacons. \\
    Were responsible for development of web server, Android app, database, and web interface.

\item[5/2014--8/2014] \textbf{\textit{Software/Hardware Development Intern}} \\
    \textit{Kalscott Eng., Lawrence, KS}\vspace{\Vspace} \\
    Designed and developed an automated air-band radio for UAVs. This system is able to predict intent of the UAV and inform nearby traffic.

\item[2/2011--6/2012] \textbf{\textit{Research Assistant}} \\
    \textit{Industrial Automation Research Center, Isfahan University of Technology, Isfahan, Iran}\vspace{\Vspace} \\
    Made a 10-channel stand-alone data logger. \\
    Designed and developed a PC-based data acquisition system for ion-mobility spectrometry.

\item[9/2010--2/2011] \textbf{\textit{Electrical Engineer}} \\
    \textit{Beh-Azmoon Co., Isfahan, Iran}\vspace{\Vspace} \\
    Created a wireless crack monitoring system for structural health monitoring %(funded by Iran's Cultural Heritage Organization, a government agency).

\item[2/2010--9/2010] \textbf{\textit{Design Engineer}} \\
    \textit{Farman Khodro Co., Isfahan, Iran}\vspace{\Vspace} \\
    Designed an electric power steering system for Iran-Khodro Samand automobile.

\item[11/2006--2/2010] \textbf{\textit{Research Assistant}} \\
    \textit{Robotics and Automotive Research Center, Isfahan University of Technology, Isfahan, Iran}\vspace{\Vspace} \\
    Developed navigation system and sensor fusion algorithm for LynCean mobile robot. \\
    Implemented a motion planning algorithm for Persia soccer robots. \\
    Implemented a walking algorithm and developed a motor controller for Parsa humanoid robot. \\
    %Designed a test bed for measuring backlash of servo motors. \\
    Prototyped an engine control unit for Honda GX35 engine. \\
    Developed an electrical dynamometer for low-power engines.

%\item[6/2010--9/2010] \textbf{\textit{Instructor}} \\
%    \textit{Isfahan University of Technology, Isfahan, Iran}\vspace{\Vspace} \\
%    Had full responsibility for instruction and assessment of a three-month summer camp on introductory robotics (programmable gates, PCB design, and CAD tools); 67 undergraduate electrical and computer engineering students attended.


\end{CV}

\section{Leadership Activities}

\begin{CV}

\item[3/2014--Present] \textbf{\textit{Active Member}} \\
    \textit{Eta Kappa Nu Honor Society - Gamma Theta Chapter}\vspace{\Vspace} \\
    Attended regular meetings and helped in voluntary services. \\

\item[10/2009--8/2010] \textbf{\textit{Hardware Development Leader}} \\
    \textit{Super-mileage Car Student Design Team}\vspace{\Vspace} \\
    Communicated status and issues to cross-functional teams and senior manager. \\
    Coordinated resources using Microsoft Project.

\item[9/2008--4/2009] \textbf{\textit{Team Leader}} \\
    \textit{NODET Rescue Robot Student Design Team}\vspace{\Vspace} \\
    Mentored students, helping them to solve problems and make decisions. \\

\end{CV}

\section{Honors and Awards}

\begin{flushleft}

National University Transportation Center Fellowship, US Department of Transportation, 2013 \vspace{\Vspace} \\
Scholarship to attend summer school on Trustworthy Cyber Infrastructure for the Power Grid, Urbana, IL, 2013 \vspace{\Vspace} \\
Fellowship from Missouri S\&T Vice-Provost for Graduate Studies, 2012 \vspace{\Vspace} \\
Gold Medal, 38\textsuperscript{th} Geneva Invention Exhibition, Switzerland, 2010 \vspace{\Vspace} \\
Best Invention Award (from Russian Incubator), 38\textsuperscript{th} Geneva Invention Exhibition, Switzerland, 2010 \vspace{\Vspace} \\
Outstanding Undergraduate Researcher Award, Isfahan University of Technology, Iran, 2009

\end{flushleft}

\ifResume
\else
\section{Refereed Conference Publications}

\begin{flushleft}
K. Marashi, S. Sedigh, and A. Hurson, ``Quantification and Analysis of Interdependency in Cyber-Physical Systems,'' \textit{In Proceedings of the 3\textsuperscript{rd} International Workshop on Reliability and Security Aspects for Critical Infrastructure Protection (ReSA4CI '16)}, Toulouse, France, Jun. 2016. \\ \vspace{\VspacePub}

K. Marashi and S. Sedigh,``Towards Comprehensive Modeling of Reliability for Smart Grids: Requirements and Challenges,''
\textit{In Proceedings of the 15\textsuperscript{th} IEEE International Symposium on High-Assurance Systems Engineering (HASE)}, pp. 105-112, Miami, FL, Jan. 2014. Selected for appearing in 2\textsuperscript{nd} issue of 2015 Science of Security Newsletter. \\ \vspace{\VspacePub}

K. Marashi, M. Woodard, S. Sedigh, and A. Hurson,``Quantitative Reliability Analysis for Intelligent Water Distribution Networks,'' \textit{In Proceedings of the Embedded Topical Meeting on Risk Management for Complex Socio-Technical Systems (RM4CSS)}, Annual Meeting of the American Nuclear Society, Washington, D.C., Nov. 2013.

\end{flushleft}
\fi

\section{Patents}

\begin{flushleft}

Wireless Temperature Monitoring System for Centrifugal Casting, Pat. No. 81750, Iran, 2014 \vspace{\Vspace} \\
2D Wireless Structural Crack Monitoring System, Pat. No. 62181, Iran, 2010 \vspace{\Vspace} \\
Handheld Data Logger for Agricultural Applications, Pat. No. 61142, Iran, 2010 \vspace{\Vspace} \\
Life Detector Robot with Adjustable Functionality, Pat. No. 60845, Iran, 2009 \vspace{\Vspace} \\
Extendable DC Motor Controller System, Pat. No. 60839, Iran, 2009 \vspace{\Vspace} \\
An Innovative Co-Axial Rotation Mechanism, Pat. No. 60847, Iran, 2009 \vspace{\Vspace} \\
Robust Track Mechanism for Locomotion of Mobile Robots, Pat. No. 60849, Iran, 2009 \vspace{\Vspace} \\
Lightweight Robust Platform for Mobile Robots, Pat. No. 60848, Iran, 2009

\end{flushleft}

\ifResume
\else
\section{Professional Activities}
\begin{flushleft}
Reviewer, Journal of Mathematics and Computer Science, 2016 \vspace{\Vspace} \\
Reviewer, IEEE International Computers, Software \& Applications Conference (COMPSAC), 2016 \vspace{\Vspace} \\
Reviewer, IEEE International Computers, Software \& Applications Conference (COMPSAC), 2015 \vspace{\Vspace} \\
Reviewer, IEEE International Green Computing Conference (IGCC), 2014 \vspace{\Vspace} \\
Reviewer, IEEE International Symposium on High Assurance Systems Engineering (HASE), 2014 \vspace{\Vspace} \\
Reviewer, IEEE International Conference on Software Security and Reliability (SERE), 2014 \vspace{\Vspace} \\
Reviewer, IEEE International Conference on Software Security and Reliability (SERE), 2013
\end{flushleft}
\fi

\ifResume
\else
\section{Professional Development}
\begin{flushleft}
Graduate Teaching Assistant Workshop, Missouri S\&T, Rolla, MO, 2014 \vspace{\Vspace} \\
Research \& Technology Development Conference, Missouri S\&T, Rolla, MO, 2014 \vspace{\Vspace} \\
Transportation Infrastructure Conference, Missouri S\&T, Rolla, MO, 2014 \vspace{\Vspace} \\
IEEE/Ameren Lean Fundamentals Workshop, Ameren, St. Louis, MO, 2014 \vspace{\Vspace} \\
Presenting Data and Information by Edward Tufte, Fairmont Chicago, Chicago, IL, 2014 \vspace{\Vspace} \\
IEEE Seminar on Modeling Cyber Attack-Defense Interactions, Missouri S\&T, Rolla, MO, 2013 \vspace{\Vspace} \\
Engineering Management \& Systems Engineering Graduate Seminar - A Survey of Applications and Future Directions of Computational Intelligence, Missouri S\&T, Rolla, MO, 2013 \vspace{\Vspace} \\
Transportation Infrastructure Conference, Capitol Plaza Hotel, Jefferson City, MO, 2013 \vspace{\Vspace} \\
Trustworthy Cyber Infrastructure for the Power Grid (TCIPG) Summer School, Q Center, St. Charles, IL, 2013
\end{flushleft}
\fi

\ifResume
\else
\section{Professional Society Membership}
\begin{flushleft}
IEEE Student Member, Since 2013 \vspace{\Vspace} \\
IEEE - Eta Kappa Nu Member, Since 2014 \vspace{\Vspace} \\
ACM Student Member, Since 2015 \vspace{\Vspace} \\
ACM - SIGMETRICS Member, Since 2015 \vspace{\Vspace} \\
National Society of Professional Engineers Student Member, Since 2015
\end{flushleft}
\fi

\section{Technical Skills}

\begin{flushleft}

\begin{tabular}{l p{\WidthSkills}}
    Programming Languages: & Python, C/C++, Java, SQL, Verilog, Assembly \\
    Web Technologies: & HTML, JavaScript, jQuery, CSS, Amazon AWS/EC2 \\
    Development Tools: & Eclipse, PyCharm, Android Studio, Git, Keil \\
    Computer Software: & LabVIEW (CLAD certificate, issued 5/13), MATLAB \& Simulink, OrCAD, \LaTeX, SAS, JMP, Active HDL, Xilinx ISE \\
    Programmable Devices: & AVR and ARM-based Microcontrollers, FPGA, CPLD \\
    Communication Protocols: & TCP/IP, 802.03, 802.11, UART, SPI, I\textsuperscript{2}C, ZigBee, Bluetooth \\
    Operating Systems: & Windows, Linux (Ubuntu, Raspbian), Android \\
    Miscellaneous: & Digital and analog circuit design, PCB design, Android application development
\end{tabular}

\end{flushleft}

\end{document}
