\section{Work Experience}
\begin{cventries}
  \cventry
    {Senior Embedded Software Engineer}
    {Romeo Power Technology}
    {Los Angeles, CA}
    {Oct. 2017 -- Present}
    {
      \begin{cvitems}
        \item Developed software requirements for a highly configurable battery management system with ISO-26262 and UL-1998 compliance.
        \item Led development of software architecture and design for a battery management system that complies with recognized functional and non-functional requirements.
        \item Designed and implemented a distributed control and decision making platform for decentralized battery management systems to improve fault tolerance and extendability.
        \item Performed research on battery control and state estimation algorithms, published several internal articles, and proposed improvements.
        \item Helped in code review process of embedded system software development for safety critical applications.
        %\item Designed and communicated procedures for unit testing, integration testing, and regression testing of battery management systems used in automotive and stationary energy storage applications.
      \end{cvitems}
    }
  \cventry
    {Graduate Research Associate}
    {Missouri S\&T, Department of Electrical and Computer Engineering}
    {Rolla, MO}
    {Aug. 2017 -- Oct. 2017}
    {
      \begin{cvitems}
        \item Assisted with research duties related to dependability modeling of critical infrastructure, including preparation of manuscripts, verification and validation of simulations, and sanity-checking of mathematical models.
      \end{cvitems}
    }
  \cventry
    {Graduate Research Assistant}
    {Missouri S\&T, Department of Electrical and Computer Engineering}
    {Rolla, MO}
    {
      Aug. 2016 -- May 2017 \linebreak\relax
      Aug. 2015 -- May 2016 \linebreak\relax
      Aug. 2014 -- May 2015 \linebreak\relax
      Aug. 2012 -- May 2014
    }
    {
      \begin{cvitems}
        \item Developed reliability, survivability, and interdependency models for the critical infrastructure. These analytical models help in identifying vulnerabilities and reducing service interruptions in different systems such as the modern electrical grid.
        %\item Made an ultra-low-power VLF signal detector for underwater communications extending battery life of transceivers by a factor of 40.
        %\item Graded homework and examinations for \emph{Digital Networks Design} course (CpE-319).
      \end{cvitems}
    }
  \cventry
    {Software/Firmware Development Intern}
    {Intellispeak LLC}
    {Lawrence, KS}
    {May 2016 -- Aug. 2016}
    {
      \begin{cvitems}
        \item Reduced power consumption of a UAV navigation system to one thirtieth of its original value and improved its performance by 40\% by migrating to a Linux-powered single-board computer and utilizing optimized algorithms.
      \end{cvitems}
    }
  \cventry
    {Full-Stack Development Intern}
    {Intellispeak LLC}
    {Lawrence, KS}
    {May 2015 -- Aug. 2015}
    {
      \begin{cvitems}
        \item Utilized Bluetooth beacons and constructed an information network to help patients with autism.
        \item Designed several test cases to identify and debug issues
        \item Responsible for development of server back-end (Python), Android app (Java), database (MySQL), and web interface (HTML, JavaScript, and CSS).
      \end{cvitems}
    }
  \cventry
    {Software/Firmware Development Intern}
    {Intellispeak LLC}
    {Lawrence, KS}
    {May 2014 -- Aug. 2014}
    {
      \begin{cvitems}
        \item Developed an automated air-band radio for UAVs. This system is able to predict intent of UAVs with 98\% accuracy and inform nearby traffic.
      \end{cvitems}
    }
  \cventry
    {Firmware Engineer}
    {Beh-Azmoon}
    {Isfahan, Iran}
    {Dec. 2011 -- Jun. 2012}
    {
      \begin{cvitems}
        \item Created a wireless digital crack monitoring system for structural health monitoring. This system can replace  traditional crack gauges and eliminate the need for constant surveillance.
      \end{cvitems}
    }
  %\cventry
%    {Control Systems Engineer}
%    {Farman Khodro}
%    {Isfahan, Iran}
%    {Feb. 2010 -- Aug. 2010}
%    {
%      \begin{cvitems}
%        \item Designed an electric power steering system for Iran-Khodro Samand automobile.
%      \end{cvitems}
%    }
  \cventry
    {Research Assistant}
    {IUT, Department of Electrical and Computer Engineering}
    {Isfahan, Iran}
    {Feb. 2006 -- Nov. 2011}
    {
      \begin{cvitems}
        \item Developed a navigation and mapping system for LynCean mobile robot by applying sensor fusion algorithms on data from a laser scanner, a GPS receiver, sonar sensors, and IR detectors.
        \item Made a multi-functional stand-alone data logger.
        \item Made a controller board for Parsa humanoid robot.
        \item Prototyped an AUTOSAR-compliant engine control unit for Honda GX35 engine.
        %\item Designed and developed a PC-based data acquisition system for ion-mobility spectrometry.
        %\item Implemented a motion planning algorithm for Persia soccer robots.
        %\item Developed an electrical dynamometer for low-power engines.
      \end{cvitems}
    }
\end{cventries} 