\section{Publications}
\subsection{Journal Papers}
\begin{cvpubs}
  \cvpub
    {\textbf{K. Marashi}, S. Sedigh, and A. Hurson, ``Identification of Interdependencies and Prediction of Fault Propagation for Cyber-Physical Systems,'' \textit{Reliability Engineering \& System Safety}, submitted.}
  \cvpub
    {M. Woodard, \textbf{K. Marashi}, and S. Sedigh, ``Survivability Evaluation and Importance Analysis for Complex Networked Systems,'' \textit{IEEE Transactions on Sustainable Computing}, under review.}
  \cvpub
    {N. Jarus, M. Woodard, \textbf{K. Marashi}, A. Faza, J. Lin, P. Maheshwari, and S. Sedigh, ``Survey on Modeling and Design of Cyber-Physical Systems,'' \textit{ACM Transactions on Cyber-Physical Systems}, under review.}
  \cvpub
    {\textbf{K. Marashi}, S. Sedigh, and A. Hurson, ``Consideration of Cyber-Physical Interdependencies in Reliability Modeling of Smart Grids,'' \textit{IEEE Transactions on Sustainable Computing}, vol. 3, no. 2, 2018.}
  \cvpub
    {\textbf{K. Marashi}, M. Woodard, S. Sedigh, and A. Hurson, ``Quantitative Reliability Analysis for Intelligent Water Distribution Networks,'' \textit{Transactions of the American Nuclear Society}, 2013.}
\end{cvpubs}

\subsection{Conference Papers}
\begin{cvpubs}
  \cvpub
    {\textbf{K. Marashi}, S. Sedigh, and A. Hurson, ``Quantification and Analysis of Interdependency in Cyber-Physical Systems,'' \textit{In Proceedings of the 46\textsuperscript{th} Annual IEEE/IFIP International Conference on Dependable Systems and Networks Workshops}, Toulouse, France, Jun. 2016.}
  \cvpub
    {\textbf{K. Marashi} and S. Sedigh, ``Towards Comprehensive Modeling of Reliability for Smart Grids: Requirements and Challenges,'' \textit{In Proceedings of the 15\textsuperscript{th} IEEE International Symposium on High-Assurance Systems Engineering (HASE)}, pp. 105-112, Miami, FL, Jan. 2014. Selected for appearing in 2\textsuperscript{nd} issue of 2015 Science of Security Newsletter.}
  \cvpub
    {\textbf{K. Marashi}, M. Woodard, S. Sedigh, and A. Hurson, ``Quantitative Reliability Analysis for Intelligent Water Distribution Networks,'' \textit{In Proceedings of the Risk Management for Complex Socio-Technical Systems}, Washington, D.C., Nov. 2013.}
\end{cvpubs}
